The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-12-05 Paper_Analyses.tex

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}{[}Christina: Works for me. I am just thinking what the
Vihman-style framework says. do you happen to know? I think the Renner
thesis discusses it.{]} {[}Katie: I wasn't really familiar with the
Vihman framework, but looking at Renner's thesis and some of the
original papers suggests that it really is about production, not
perception.{]}

@@

\begin{figure}
\centering
\includegraphics{figures/PRISMA_MA_Mispronunciation.png}
\caption{}
\end{figure}

@@

{[}Christina: I needed to move this around because we first need to say
that we could not compute some effect sizes and removed outlierts.{]}

@@

{[}Katie{]} Do you want number of records and papers for the imputed
correlations as well? You've put a -1, assuming there was something
wrong with one of the papers or something like that? How does that shake
out for number of records? {[}Christina: No clue what the -1 was,
sorry.{]}

@@

{[}Christina: In the above 2 paragraphs I got confused, should it be
present or past. I think it switched in the las tparagraph so I started
to adapt, but I think it would be best for you to decide. {]}{[}Katie:
Good catch. I've gone through the Methods section and changed everything
to past, per APA guidelines.{]}

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to some baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; we used
the baseline reported by the authors of each paper. Most papers
(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
pre-naming phase from the PTL score for a post-naming phase and report a
difference score.

Other papers either compared post- and pre-naming PTL with one another
(\emph{n} = 29 records from 10 papers), thus reporting two variables, or
compared post-naming PTL with a chance level of 50\%, (\emph{n} = 23
records from 9 papers). For all these comparisons, positive values
(either as reported or after subtraction of chance level or a pre-naming
PTL) indicate target looks towards the target object after hearing the
label, i.e.~a recognition effect. Standardized effect sizes based on
mean differences, as calculated here, preserve the sign. Consequently,
positive effect sizes reflect more looks to the target picture after
naming, and larger positive effect sizes indicate comparatively more
looks to the target.

@@

\subsection{(Insert Figure 2 about
here)}\label{insert-figure-2-about-here-1}

@@

{[}Christina{]} Can you try and align the axes for both plots?
{[}Katie{]} I can, but then the dotted line doesn't extend the full way
(which I think is quite ugly). Not sure how to fix that.

@@

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 10 experimental conditions, with correlation
values ranging from -0.16 to 0.48. The mean effect size Pearson's
\emph{r} of 0.14 was small but did differ significantly from zero (CI
{[}0.03; 0.25{]} \emph{p} = 0.012). However, the lower bound of the CI
is close to zero and considering the small sample size, one might
hypothesize that with more power the small relationship might become
even larger. As a result, we can draw a tentative conclusion that there
is a positive relationship between comprehension scores and object
recognition in response to correct pronunciations.

{[}Christina{]} It's significant now! {[}Katie{]} Must be because you
removed the outliers. I've changed around the wording :)

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 29 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.05 was small and did not differ significantly from zero
(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation and large
variances suggest a lack of relationship between vocabulary and object
recognition for mispronunciations. We again emphasize that we cannot
draw a firm conclusion due to the small number of studies we were able
to include here.

Figure 4 plots the year of publication for all the mispronunciation
sensitivity studies included in this meta-analysis. This figure
illustrates two things: the growing number of mispronunciation
sensitivity studies and the waning number of studies measuring
vocabulary. The lack of evidence for a relationship between
mispronunciation sensitivity and vocabulary size in early studies may
have contributed to increasingly fewer researchers including vocabulary
measurements in their mispronunciation sensitivity experimental design.
This may explain our underpowered analysis of the relationship between
mispronunciation sensitivity and vocabulary size.

@@

In a typical trial in a mispronunciation sensitivity study, the
target-distractor image pairs are first presented in silence, followed
by auditory presentation of a carrier phrase or isolated presentation of
the target word (correctly pronounced or mispronounced). When designing
mispronunciation sensitivity studies, experimenters can choose the
length of time each trial is presented. This includes both the length of
time before the target object is named (pre-naming phase) as well as
after (post-naming phase) and is determined prior to data collection. To
examine the size of the time window analyzed in the post-naming phase,
we must first consider overall length of time post-naming, because it
limits the overall time window available to analyze and might thus
predict which time window was analyzed. Across papers, actual
post-naming phase length varied from 2000 to 9000 ms, with a median
value of 3500 ms. We note that the most popular actual post-naming phase
length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
was an inverse relationship between infant age and actual post-naming
phase length, such that younger infants were presented with longer a
longer post-naming phase, although this correlation was not significant
(\emph{r} = 0.01, \emph{p} = 0.882). Presumably, younger infants may be
exposed to longer trials because their word recognition abilities are
expected to be slower than older infants (Fernald et al., 1998).

Unlike the actual post-naming phase length, the size of the post-naming
time window analyzed can be chosen after the experimental data is
collected. Interestingly, half of the experimental conditions were
analyzed using the same length of post-naming phase as the infant heard
in the actual experiment (124), while the other half were analyzed using
a shorter length of post-naming phase, excluding later portions of the
post-naming phase (127). Across papers, the length of the post-naming
phase analyzed varied from 1510 to 4000 ms, with a median value of 2500
ms. We note that the most popular actual post-naming phase length was
2000 ms, used in \emph{n} = 97 experimental conditions. Similar to
actual post-naming phase length, there was an inverse relationship
between infant age and the size of the post-naming time window analyzed,
such that younger infants' looking times were analyzed using a longer
post-naming time window, here the relationship was significant (\emph{r}
= -0.23, \emph{p} \textless{} .001). Again, the choice to analyze a
shorter post-naming time window is likely related to evidence that speed
of processing is slower in younger infants (Fernald et al., 1998). To
summarize, we observe variation in time-related aspects related to
infants' age. This variation is most pronounced, and even significant,
for the time window that is being analyzed after the target label has
been heard.

Another potential source of variation in studies that analyze
eye-movements is the amount of time it takes for an eye movement to be
initiated in response to a visual stimulus, which we refer to as offset
time. Previous studies examining simple stimulus response latencies
first determined that infants require at least 233 ms to initiate an
eye-movement in response to a stimulus (Canfield \& Haith, 1991). In the
first infant mispronunciation sensitivity study, Swingley and Aslin
(2000) used an offset time of 367 ms, which was \enquote{an
\enquote{educated guess} based on studies\ldots{} showing that target
and distractor fixations tend to diverge at around 400 ms.} (Swingley \&
Aslin, 2000, p.~155). Upon inspecting the offset time values used in the
papers in our meta-analysis, the majority used a similar offset time
value (between 360 and 370 ms) for analysis (\emph{n} = 151), but offset
values ranged from 0 to 500 ms, and were not reported for 36
experimental conditions. We note that Swingley (2009) also included
offset values of 1133 ms to analyze responses to coda mispronunciations.
There was an inverse relationship between infant age and size of offset,
such that younger infants were given longer offsets, although this
correlation was not significant (\emph{r} = -0.10, \emph{p} = 0.13).
This lack of a relationship is possibly driven by the field's consensus
that an offset of about 367 ms is appropriate for analyzing word
recognition with PTL measures, including studies that evaluate
mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time
window (infant age) or offset time (previous studies), these choices may
occur after data collection and might therefore lead to a higher rate of
false-positives (Gelman, A., \& Loken, E. (2013). Considering that these
choices were systematically different across infant ages, at least for
the post-naming time window, we next explored whether the size of time
window analyzed or the offset time influenced sensitivity to
mispronunciations.

@@

We first assessed whether size of the post-naming time window analyzed
had an impact on the overall size of the reported mispronunciation
sensitivity. We considered data from both conditions in a joint analysis
and included condition (correct pronunciation, mispronunciation) as an
additional moderator. The moderator test was significant, QM(3) =
236.958, \emph{p} \textless{} .001. The estimate for the interaction
between post-naming phase size and condition was small but significant
\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
\textless{} .001. This relationship is plotted in Figure 3a. The results
suggest that the size of the post-naming phase analyzed significantly
impacted mispronunciation sensitivity. Specifically, the difference
between target fixations for correctly pronounced and mispronounced
items (mispronunciation sensitivity) was significantly greater when the
post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the
post-naming time window analyzed and infant age, such that younger ages
had a longer window of analysis, we next examined whether the size of
post-naming time window analyzed modulated the development of
mispronunciation sensitivity. We merged the two datasets and included
condition (correct pronunciation, mispronunciation) as well as age as
additional moderators. The moderator test was significant QM(7) =
247.322, \emph{p} \textless{} .001. The estimate for the
three-way-interaction between condition, size of post-naming phase, and
age was small, but significant (\(\beta\) = = -0.04, SE = 0.014, 95\%
CI{[}-0.068, -0.012{]}, \emph{p} = 0.006. As can be seen in Figure 3b,
smaller post-naming time window size leads to greater increases in
mispronunciation sensitivity with development. For example, when
experimental conditions were analyzed with a post-naming time window of
2000 ms or less, mispronunciation sensitivity is found to increase with
infant age. If the post-naming time window analyzed is greater than 2000
ms, however, there is no or a negative relation of mispronunciation
sensitivity and age. In other words, all three possible hypotheses might
be supported depending on analysis choices made regarding the size of
the post-naming time window to analyze. This is especially important,
considering that our key question is how mispronunciation sensitivity
changes with development. These results suggest that conclusions about
the relationship between infant age and mispronunciation sensitivity may
be mediated by the size of the post-naming time window analyzed.

@@

We next assessed whether the time between the target was named and the
start of the analysis, namely offset time, had an impact on the size of
the reported mispronunciation sensitivity. When we included both
condition and offset time as moderators, the moderator test was
significant, QM(3) = 236.958, \emph{p} \textless{} .001, but the
estimate for the interaction between offset time and condition was
almost zero \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
0.505. Although we found no relationship between offset time and infant
age, we also examined whether the size of offset time modulated the
development of mispronunciation sensitivity. When both offset time and
condition were included as moderators, the moderator test was
significant QM(7) = 200.867, \emph{p} \textless{} .001, but the
three-way-interaction between condition, offset time, and age was very
small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
\emph{p} = 0.605. Taken together, these results suggest that offset time
does not modulate mispronunciation sensitivity. There is no relationship
between offset time and age, and we find no influence of offset time on
the development of mispronunciation sensitivity.

@@

Mispronunciation studies evaluate infants' proportion of target looks
(PTL) in response to correct and mispronounced words. Experiments
typically include a phase where no naming event has occured, whether
correctly pronounced or mispronounced, which we refer to as the
baseline. The purpose of the baseline is to ensure that infants do not
have systematic preferences for the target or distractor (greater
interest in a cat compared to a cup) which may drive PTL scores in the
post-naming phase. As described in the Data Analysis sub-section of the
Methods, there was considerable variation across papers in way that
baseline was calculated, resulting in different measured outcomes or
dependent variables. Over half of the experimental conditions (\emph{n}
= 129) subtracted the PTL score for a pre-naming phase from the PTL
score for a post-naming phase. This results in one value, which is then
compared with a chance value of 0. When positive, this indicates that
infants increased their looks to the target after hearing the naming
label (correct or mispronounced) relative to the pre-naming baseline
PTL. We will refer to this dependent variable as the Difference Score.
Another dependent variable, which was used in 69 experimental
conditions, directly compared the post- and pre-naming PTL scores with
one another. This requires two values, one for the pre-naming phase and
one for the post-naming phase. A greater post compared to pre-naming
phase PTL indicates that infants increased their target looks after
hearing the naming label. We will refer to this dependent variable as
Pre vs.~Post. Finally, the remaining 53 experimental conditions compared
the post-naming PTL score with a chance value of 50\%. Here, the
infants' pre-naming phase preferences are not considered and instead
target fixations are evaluated based on the likelihood to fixate one of
two pictures. We will refer to this dependent variable as Post.

The Difference Score and Pre vs.~Post can be considered similar to one
another, in that they are calculated on the same type of data and
consider pre-naming preferences. The Post dependent variable, in
contrast, does not consider pre-naming preferences. To our knowledge,
there is no theory or evidence that explicitly drives choice of
dependent variable in analysis of mispronunciation sensitivity, which
may explain the wide variation in dependent variable reported in the
papers included in this meta-analysis. We next explored whether the type
of dependent variable calculated influenced sensitivity to
mispronunciations. Considering that the dependent variable Post differs
in its consideration of pre-naming preferences, we directly compared
mispronunciation sensitivity between Post as a reference condition and
both Difference Score and Pre vs.~Post dependent variables.

We first assessed whether the choice of dependent variable had an impact
on the size of mispronunciation sensitivity. When we included both
condition and dependent variable as moderators, the moderator test was
significant QM(5) = 259.817, \emph{p} \textless{} .001. The estimate for
the interaction between Pre vs.~Post and condition was significantly
smaller than that of the Post dependent variable (\(\beta\) = -0.392, SE
= 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p} \textless{} .001), but the
difference between the Difference Score and Post in the interaction with
condition was small and not significant (\(\beta\) = -0.01, SE = 0.098,
95\% CI{[}-0.203, 0.183{]}, \emph{p} = 0.916). This relationship is
plotted in Figure 4a. The results suggest that dependent variable
calculated significantly impacted the size fo the mispronunciation
sensitivity effect, such that Post. vs.~Pre showed a smaller
mispronunciation sensitivity effect than Post, but no difference between
the Difference Score and Post.

We next examined whether the type of dependent variable calculated
modulated the development of mispronunciation sensitivity. When age was
included as an additional moderator, the moderator test was significant
QM(11) = 273.585, \emph{p} \textless{} .001. The estimate for the
interaction between Pre vs.~Post, condition, and age was significantly
smaller than that of the Post dependent variable (\(\beta\) = -0.089, SE
= 0.03, 95\% CI{[}-0.148, -0.03{]}, \emph{p} = 0.003), but the
difference between the Difference Score and Post in the interaction with
condition and age was small and not significant (\(\beta\) = -0.036, SE
= 0.027, 95\% CI{[}-0.088, 0.016{]}, \emph{p} = 0.174). This
relationship is plotted in Figure 4b. When the dependent variable was
Pre vs.~Post, mispronunciation sensitivity decreased with infant age,
while in comparison, when the dependent variable was Post,
mispronunciation sensitivity increased with infant age. There was no
difference in mispronunciation sensitivity change with infant
development between the Post and Difference Score dependent variables.
Similar to size of post-naming time window analyzed, all three possible
developmental hypotheses might be supported depending on the dependent
variable reported. In other words, choice of dependent variable may
influence the conclusion drawn regarding how mispronunciation
sensitivity may change with infant age.

@@

@@

Overall, infants showed reliable correct object recognition when given
both correctly pronounced and mispronounced labels. In other words, not
only did infants correctly recognize object labels when they were
correctly pronounced, they also were likely to accept mispronunciations
as acceptable labels for targets. Mispronounced labels were considered a
better match for target images than a distractor image, despite the
differences in the phonological form of correctly pronounced and
mispronounced words. Nonetheless, there was a considerable difference in
target fixations in response to correctly pronounced and mispronounced
labels, suggesting overall mispronunciation sensitivity in the current
experimental literature.

We next evaluated the developmental trajectory of infants'
mispronunciation sensitivity. Based on previous theoretical accounts and
existing experimental evidence, we envisioned three possible
developmental patterns: increasing sensitivity, decreasing sensitivity,
and unchanging sensitivity. We observed no influence of age when it was
considered as a moderator of mispronunciation sensitivity. Of the two
mainstream theories identified in our literature review, neither the
Perceptual Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \&
Werker, 2007; Werker \& Curtin, 2005) account for a lack of
developmental change. The results of our meta-analysis are supported by
a handful of studies directly comparing infants over a range of ages
(Swingley \& Aslin, 2000; Bailey \& Plunkett, 2002; Zesiger et al.,
2012), which also found no developmental change in mispronunciation
sensitivity.

>>>>

@@

\subsection{(Insert Figure 1 about
here)}\label{insert-figure-1-about-here}

\begin{figure}
\centering
\includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
\caption{}
\end{figure}

@@

@@

@@

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to some baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; we used
the baseline reported by the authors of each paper. Most papers
(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
pre-naming baseline phase from the PTL score for a post-naming phase and
report a difference score.

Other papers either compared post- and pre-naming PTL with one another
(\emph{n} = 29 records from 10 papers), thus reporting two variables, or
compared post-naming PTL with a chance level of 50\%, (\emph{n} = 23
records from 9 papers). For all these comparisons, positive values
(either as reported or after subtraction of chance level or a pre-naming
baseline PTL) indicate target looks towards the target object after
hearing the label, i.e.~a recognition effect. Standardized effect sizes
based on mean differences, as calculated here, preserve the sign.
Consequently, positive effect sizes reflect more looks to the target
picture after naming, and larger positive effect sizes indicate
comparatively more looks to the target.

@@

@@

@@

We first considered the relationship between vocabulary and object
recognition for correct pronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 9 of 10 experimental conditions, with correlation
values ranging from -0.16 to 0.48. The mean effect size Pearson's
\emph{r} of 0.14 was small but did differ significantly from zero (CI
{[}0.03; 0.25{]} \emph{p} = 0.012). As a result, we can draw a tentative
conclusion that there is a positive relationship between comprehension
scores and object recognition in response to correct pronunciations.

We next considered the relationship between vocabulary and object
recognition for mispronunciations. Higher comprehension scores were
associated with greater object recognition in response to correct
pronunciations for 17 of 29 experimental conditions, with correlation
values ranging from -0.35 to 0.57. The mean effect size Pearson's
\emph{r} of 0.05 was small and did not differ significantly from zero
(CI {[}-0.01; 0.12{]} \emph{p} = 0.119). The small correlation suggests
a lack of relationship between vocabulary and object recognition for
mispronunciations. We again emphasize that we cannot draw a firm
conclusion due to the small number of studies we were able to include
here.

Figure 4 plots the year of publication for all the mispronunciation
sensitivity studies included in this meta-analysis. This figure
illustrates two things: the growing number of mispronunciation
sensitivity studies and the waning number of studies measuring
vocabulary. The lack of evidence for a relationship between
mispronunciation sensitivity and vocabulary size in some early studies
may have contributed to increasingly fewer researchers including
vocabulary measurements in their mispronunciation sensitivity
experimental design. This may explain our underpowered analysis of the
relationship between mispronunciation sensitivity and vocabulary size.

@@

In a typical trial in a mispronunciation sensitivity study, the
target-distractor image pairs are first presented in silence, followed
by auditory presentation of a carrier phrase or isolated presentation of
the target word (correctly pronounced or mispronounced). When designing
mispronunciation sensitivity studies, experimenters can choose the
length of time each trial is presented. This includes both the length of
time before the target object is named (pre-naming phase) as well as
after (post-naming phase) and is determined prior to data collection. To
examine the size of the time window analyzed in the post-naming phase,
we must first consider overall length of time post-naming, because it
limits the overall time window available to analyze and might thus
predict which time window was analyzed. Across papers, actual
post-naming phase length varied from 2000 to 9000 ms, with a median
value of 3500 ms. We note that the most popular actual post-naming phase
length was 4000 ms, used in \emph{n} = 74 experimental conditions. There
was no apparent relation between infant age and overall post-naming
phase duration (\emph{r} = 0.01, 95\% CI{[}-0.11, 0.13{]}, \emph{p} =
0.882).

Unlike the actual post-naming phase length, the size of the post-naming
time window analyzed can be chosen after the experimental data is
collected. Interestingly, half of the experimental conditions were
analyzed using the same length of post-naming phase as the infant heard
in the actual experiment (124), while the other half were analyzed using
a shorter portion of the post-naming phase, usually excluding later
portions (127). Across papers, the length of the post-naming phase
analyzed varied from 1510 to 4000 ms, with a median value of 2500 ms. We
note that the most popular actual post-naming phase length was 2000 ms,
used in \emph{n} = 97 experimental conditions. There was an inverse
relationship between infant age and the size of the post-naming time
window analyzed, such that younger infants' looking times were analyzed
using a longer post-naming time window, here the relationship was
significant (\emph{r} = -0.23, 95\% CI{[}-0.35, -0.11{]}, \emph{p}
\textless{} .001). The choice to analyze a shorter post-naming time
window is likely related to evidence that speed of processing is slower
in younger infants (Fernald et al., 1998). To summarize, we observe
variation in time-related aspects related to infants' age.

{[}Christina: Below there is a \ldots{}. Just so we don't forget
it.{]}{[}Katie: I put it in there on purpose, I'm quoting directly from
the paper, but the original sentence doesn't make full sense in this
context, so I cut out the part that doesn't fit. This is the original
sentence: \enquote{The lower bound of 367 ms is an `educated guess'
based on studies such as those cited above, and our data (here and in
other studies) showing that target and distractor fixations tend to
diverge at around 400 ms.}{]}

Another potential source of variation in studies that analyze
eye-movements is the amount of time it takes for an eye movement to be
initiated in response to a visual stimulus, which we refer to as offset
time. Previous studies examining simple stimulus response latencies
first determined that infants require at least 233 ms to initiate an
eye-movement in response to a stimulus (Canfield \& Haith, 1991). In the
first infant mispronunciation sensitivity study, Swingley and Aslin
(2000) used an offset time of 367 ms, which was \enquote{an
\enquote{educated guess} based on studies . . . showing that target and
distractor fixations tend to diverge at around 400 ms.} (Swingley \&
Aslin, 2000, p.~155). Upon inspecting the offset time values used in the
papers in our meta-analysis, the majority used a similar offset time
value (between 360 and 370 ms) for analysis (\emph{n} = 151), but offset
values ranged from 0 to 500 ms, and were not reported for 36
experimental conditions. We note that Swingley (2009) also included
offset values of 1133 ms to analyze responses to coda mispronunciations.
There was an inverse relationship between infant age and size of offset,
such that younger infants were given longer offsets, although this
correlation was not significant (\emph{r} = -0.10, \emph{p} = 0.13).
This lack of a relationship is possibly driven by the field's consensus
that an offset of about 367 ms is appropriate for analyzing word
recognition with PTL measures, including studies that evaluate
mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time
window (infant age) or offset time (previous studies), these choices may
occur after data collection and might therefore lead to a higher rate of
false-positives (Gelman \& Loken, 2013). Considering that these choices
were systematically different across infant ages, at least for the
post-naming time window analyzed, we next explored whether the size of
time window analyzed or the offset time influenced sensitivity to
mispronunciations.

@@

We first assessed whether size of the post-naming time window analyzed
had an impact on the overall size of the reported mispronunciation
sensitivity. We considered data from both conditions in a joint analysis
and included condition (correct pronunciation, mispronunciation) as an
additional moderator. The moderator test was significant (QM(3) =
236.958, \emph{p} \textless{} .001). The estimate for the interaction
between post-naming phase size and condition was small but significant
(\(\beta\) = -0.262, SE = 0.059, 95\% CI{[}-0.377, -0.148{]}, \emph{p}
\textless{} .001). This relationship is plotted in Figure 3a. The
results suggest that the size of the post-naming phase analyzed
significantly impacted mispronunciation sensitivity. Specifically, the
difference between target fixations for correctly pronounced and
mispronounced items (mispronunciation sensitivity) was significantly
greater when the post-naming phase was shorter.

Considering that we found a significant relationship between the length
of the post-naming time window analyzed and infant age, such that
younger ages had a longer window of analysis, we next examined whether
the size of post-naming time window analyzed modulated the estimated
size of mispronunciation sensitivity as infant age changed. We therefore
included age as additional moderator of the previous analysis. The
moderator test was significant (QM(7) = 247.322, \emph{p} \textless{}
.001). The estimate for the three-way-interaction between condition,
size of post-naming phase, and age was small, but significant (\(\beta\)
= = -0.04, SE = 0.014, 95\% CI{[}-0.068, -0.012{]}, \emph{p} = 0.006).
As can be seen in Figure 3b, smaller post-naming time window size leads
to greater increases in measured mispronunciation sensitivity with
development. For example, when experimental conditions were analyzed
with a post-naming time window of 2000 ms or less, mispronunciation
sensitivity is found to increase with infant age. If the post-naming
time window analyzed is greater than 2000 ms, however, there is no or a
negative relation of mispronunciation sensitivity and age. In other
words, all three possible developmental hypotheses might be supported
depending on analysis choices made regarding the size of the post-naming
time window to analyze. This is especially important, considering that
our key question is how mispronunciation sensitivity changes with
development. These results suggest that conclusions about the
relationship between infant age and mispronunciation sensitivity may be
mediated by the size of the post-naming time window analyzed.

@@

We next assessed whether the time between the target was named and the
start of the analysis, namely offset time, had an impact on the size of
the reported mispronunciation sensitivity. When we included both
condition and offset time as moderators, the moderator test was
significant (QM(3) = 236.958, \emph{p} \textless{} .001), but the
estimate for the interaction between offset time and condition was
almost zero (\(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p} =
0.505). Although we found no relationship between offset time and infant
age, we also examined whether the size of offset time modulated the the
measure of mispronunciation sensitivity over infant age. When both
offset time and condition were included as moderators, the moderator
test was significant (QM(7) = 200.867, \emph{p} \textless{} .001), but
the three-way-interaction between condition, offset time, and age was
very small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0,
0{]}, \emph{p} = 0.605. Taken together, these results suggest that
offset time does not modulate measured mispronunciation sensitivity.
There is no relationship between offset time and age, and we find no
influence of offset time on the estimated size of mispronunciation
sensitivity over age.

@@

Mispronunciation studies evaluate infants' proportion of target looks
(PTL) in response to correct and mispronounced words. Experiments
typically include a phase where no naming event has occured, whether
correctly pronounced or mispronounced, which we refer to as the
pre-naming phase The purpose of the pre-naming phase is to ensure that
infants do not have systematic preferences for the target or distractor
(greater interest in a cat compared to a cup) which may drive PTL scores
in the post-naming phase. As described in the Data Analysis sub-section
of the Methods, however, there was considerable variation across papers
in whether this pre-naming phase was used as a baseline measurement, or
whether a different baseline measurement was used. This resulted in
different measured outcomes or dependent variables. Over half of the
experimental conditions (\emph{n} = 129) subtracted the PTL score for a
pre-naming phase from the PTL score for a post-naming phase. This
results in one value, which is then compared with a chance value of 0.
When positive, this indicates that infants increased their looks to the
target after hearing the naming label (correct or mispronounced)
relative to the pre-naming baseline PTL. We will refer to this dependent
variable as the Difference Score. Another dependent variable, which was
used in 69 experimental conditions, directly compared the post- and
pre-naming PTL scores with one another. This requires two values, one
for the pre-naming phase and one for the post-naming phase. A greater
post compared to pre-naming phase PTL indicates that infants increased
their target looks after hearing the naming label. We will refer to this
dependent variable as Pre vs.~Post. Finally, the remaining 53
experimental conditions compared the post-naming PTL score with a chance
value of 50\%. Here, the infants' pre-naming phase baseline preferences
are not considered and instead target fixations are evaluated based on
the likelihood to fixate one of two pictures. We will refer to this
dependent variable as Post.

The Difference Score and Pre vs.~Post can be considered similar to one
another, in that they are calculated on the same type of data and
consider pre-naming preferences. {[}Christina: adding sth here{]}. It
should be noted, however, that the Difference Score can better counter
act participant- and item-level differences, whereas Pre vs.~Post is a
group-level measure. The Post dependent variable, in contrast, does not
consider pre-naming baseline preferences. To our knowledge, there is no
theory or evidence that explicitly drives choice of dependent variable
in analysis of mispronunciation sensitivity, which may explain the wide
variation in dependent variable reported in the papers included in this
meta-analysis. We next explored whether the type of dependent variable
calculated influenced the estimated size of sensitivity to
mispronunciations. Considering that the dependent variable Post differs
in its consideration of pre-naming baseline preferences, substituting
these for a chance value, we directly compared mispronunciation
sensitivity between Post as a reference condition and both Difference
Score and Pre vs.~Post dependent variables.

We first assessed whether the choice of dependent variable had an impact
on the size of estimated mispronunciation sensitivity. When we included
both condition and dependent variable as moderators, the moderator test
was significant (QM(5) = 259.817, \emph{p} \textless{} .001). The
estimate for the interaction between Pre vs.~Post and condition was
significantly smaller than that of the Post dependent variable
(\(\beta\) = -0.392, SE = 0.101, 95\% CI{[}-0.59, -0.194{]}, \emph{p}
\textless{} .001), but the difference between the Difference Score and
Post in the interaction with condition was small and not significant
(\(\beta\) = -0.01, SE = 0.098, 95\% CI{[}-0.203, 0.183{]}, \emph{p} =
0.916). This relationship is plotted in Figure 4a. The results suggest
that the reported dependent variable significantly impacted the size of
the estimated mispronunciation sensitivity effect, such that studies
reporting the Post. vs.~Pre dependent variable showed a smaller
mispronunciation sensitivity effect than those reporting Post, but that
there was no difference between the Difference Score and Post dependent
variables.

We next examined whether the type of dependent variable calculated
modulated the the estimated change in mispronunciation sensitivity over
infant age. When age was included as an additional moderator, the
moderator test was significant (QM(11) = 273.585, \emph{p} \textless{}
.001). The estimate for the interaction between Pre vs.~Post, condition,
and age was significantly smaller than that of the Post dependent
variable (\(\beta\) = -0.089, SE = 0.03, 95\% CI{[}-0.148, -0.03{]},
\emph{p} = 0.003), but the difference between the Difference Score and
Post in the interaction with condition and age was small and not
significant (\(\beta\) = -0.036, SE = 0.027, 95\% CI{[}-0.088, 0.016{]},
\emph{p} = 0.174). This relationship is plotted in Figure 4b. When the
dependent variable reported was Pre vs.~Post, mispronunciation
sensitivity was found to decrease with infant age, while in comparison,
when the dependent variable was Post, mispronunciation sensitivity was
found to increase with infant age. There was no difference in the
estimated mispronunciation sensitivity change with infant age between
the Post and Difference Score dependent variables.

Similar to size of post-naming time window analyzed, all three possible
developmental hypotheses might be supported depending on the dependent
variable reported. In other words, choice of dependent variable may
influence the conclusion drawn regarding how mispronunciation
sensitivity may change with infant age.

@@

\subsection{Controlling for analysis
choices}\label{controlling-for-analysis-choices}

{[}Christina: Do you want to add this section?{]}{[}Katie: From what I
came up with, it makes no difference to the conclusions we make in the
regular models. But, I am not sure I did it right. I don't really feel
like they have to be included, but if you think it would be good, then
we can work on it.{]}

@@

Overall, the results of the meta-analysis showed that infants reliably
fixate the target object when given both correctly pronounced and
mispronounced labels. In other words, not only did infants recognize
object labels when they were correctly pronounced, they also were likely
to accept mispronunciations as acceptable labels for targets.
Mispronounced labels were considered a better match for target images
than a distractor image, despite the differences in the phonological
form of correctly pronounced and mispronounced words. Nonetheless, there
was a considerable difference in target fixations in response to
correctly pronounced and mispronounced labels, suggesting overall
mispronunciation sensitivity in the current experimental literature. In
short, infants show knowledge of what constitutes unacceptable variation
in word forms, displaying knowledge of the role of phonemic changes
throughout the ages assessed here. At the same time, infants, like
adults, can recover from mispronunciations.

We next evaluated the developmental trajectory of infants'
mispronunciation sensitivity. Based on previous theoretical accounts and
existing experimental evidence, we envisioned three possible
developmental patterns: increasing, decreasing, and unchanging
sensitivity. We observed no influence of age when it was considered as a
moderator of mispronunciation sensitivity. Of the two mainstream
theories identified in our literature review, neither the Perceptual
Attunement account (Best 1994, 1995) nor PRIMIR (Curtin \& Werker, 2007;
Werker \& Curtin, 2005) account for a lack of developmental change. The
results of our meta-analysis are supported by a handful of studies
directly comparing infants over a range of ages (Swingley \& Aslin,
2000; Bailey \& Plunkett, 2002; Zesiger et al., 2012), which also found
no developmental change in mispronunciation sensitivity.

Both the Perceptual Attunement (Best 1994, 1995) and PRIMIR (Curtin \&
Werker, 2007; Werker \& Curtin, 2005) accounts link a change of
mispronunciation sensitivity specifically with vocabulary growth, in
comparison to development in general. Vocabulary growth leads to an
increase (PRIMIR; Curtin \& Werker, 2007; Werker \& Curtin, 2005) or
decrease (Perceptual Attunement; Best 1994, 1995) in mispronunciation
sensitivity and vocabulary is expected to grow considerably in the age
range considered in the current meta-analysis (see
wordbank.stanford.edu; Frank et al., 2017). The lack of developmental
effects found in our meta-analysis may therefore be due to using age,
instead of vocabulary growth, as a facilitator for change in
mispronunciation sensitivity. Yet, an analysis of correlations between
vocabulary size and object recognition effect sizes does not support
this argument. Although an increasing vocabulary size lead to increased
object recognition for correctly pronounced words, this was not the case
for mispronunciations. Some previous experimental evidence also supports
a lack of a relationship between vocabulary size and mispronunciation
sensitivity (e.g.~Mani \& Plunkett, 2007; Swingley \& Aslin, 2000; Tao
et al., 2012; but see Mani \& Plunkett, 2010). This would suggest that
object recognition for mispronunciations is not modulated by vocabulary
size, contrary to the predictions of the Perceptual Attunement (Best
1994, 1995) and PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005)
accounts and further supporting the overall lack of an influence of age
on mispronunciation sensitivity.
